Identity Blockchain - Proof of Identity

### 2022-06-28 paper.tex
updated pages 1-3, 6

\documentclass{article}
%\documentclass[twocolumn]{article}%
\usepackage[utf8]{inputenc}%
\usepackage{standalone}%
\usepackage{amsmath}%
\usepackage{amsthm}%
\usepackage{amssymb}%
\usepackage{hyperref}%
\usepackage{xcolor}%
\usepackage{tabularx}%
\usepackage{listings}%
\lstdefinestyle{b}{basicstyle=\tiny\ttfamily}
\lstset{
  showspaces=false,
  showstringspaces=false
  }

% Add your keywords here, and have this in a separate file
% and include it in your preamble
\lstset{emph={%
    function, uint256, public, mapping,contract,bytes,bool, if, for,
    field, private, def, import, assert, require, zksnarkverify %
},emphstyle={\color{blue}\bfseries}%
}

%\definecolor{keywords}{HTML}{8A4A0B}
%
%\definecolor{background}{HTML}{EEEEEE}
%
%\lstset{language=[LaTeX]Tex,
%    keywordstyle=\color{keywords},
%    keywordstyle=[2]\color{red},
%    keywordstyle=[3]\color{orange},
%    basicstyle=\normalfont\ttfamily,
%    showstringspaces=false,
%    frameround=ftff,
%    frame=lines,
%    morekeywords={RequirePackage,ProvidesPackage},
%    keywords=[2]{Some,Other,Keywords},
%    keywords=[3]{and,another,test},
%    backgroundcolor=\color{background}
%}

@@

\title{Proof of Identity}
\author{
Albert Vučinović, University North\\
Miroslav Jerković, University of Zagreb
}
\begin{document}
\maketitle
\section{Notation}
\begin{tabular}{p{0.36\linewidth}|p{0.55\linewidth}}
  $(K, K^{-1})$ & A pair of public $K$ and the corresponding private key $K^{-1}$. \\
	$K(value)$ & $value$ encrypted with a public key $K$. \\
	$K^{-1}(value)$ & $value$ encrypted with a private key $K^{-1}$. \\
  $H$ & Hash function, e.g. some zksnark friedly one \\
	$\kid$ &  State CA certified public key of e.g. eID\\
  $\khk$ & Person key, public key used to access \pbc{} as an unknown Person. \\
  $Nin$ & A personal National Identification Number issued by state.
\end{tabular}

@@

\newpage
\section{Registering $\khk$ (Person key)}
\begin{enumerate}
  \item Register $\kid$ on \pbc, by calling 
    $$register\kid(Nin, \kid^{-1}("register\kid"), proofNinOwnsK).$$

    The Person tells the \pbc{} what personal identification document will they be using.

    What is the meaning behind $register\kid$ function?
    \begin{itemize}
      \item Sybil resistance. To prevent a Person from registering more than one $\khk$ using different identification documents, which are issued for the same $Nin$.
      \item Loss of $\kid$. If a Person looses previously registered $\kid$ (e.g. by loosing the eID), they can register a new one.
      \item Identity theft damage control. If a Person overwrites the previous $\kid$ with a new one, the identity thief will loose access to services that check the whole identity chain.
    \end{itemize}

    Entities who know $\kid$ (e.g. CA that issued it) can know that the Person is using \pbc{}, and what identification document the Person is using.

  \item Register $\khk$ on \pbc, by calling 
    $$register\khk(Nin\kid, Nin\kid\khk, proof)$$
  where:
    \begin{enumerate}
      \item $Nin\kid=H(Nin,\kid^{-1}("register\khk"))$
      \item $Nin\kid\khk=H(Nin, \kid^{-1}("register\khk"), \khk^{-1}("register\khk"))$
    \end{enumerate}
\end{enumerate}

\newpage
\section{On chain code}
\begin{lstlisting}[language=C, frame=single, style=b]
//pseudo Solidity
//Key is eID private key, or PrivateeIDKey("")
//PersonKey is Blockchain key used by a Person
contract IdentitiesManager {
  //all the mappings are mappings where uint256 is a hash!
  mapping(uint256 => uint256) public PinKUsed;
  mapping(uint256 => uint256) public PinKPUsed;
  mapping(uint256 => uint256) public PinKPLastConfirmed;
  mapping(uint256 => bool) public PInvalid;
  mapping(uint256 => bool) public KInvalid;
  //TODO:CA fields!

  //K_1=K_1("registerK")
  //Pin=H(Pin)
  function registerK public(
    uint256 Pin,
    uint256 K_1,
    bytes proofPinOwnsK
  ){
    uint256 previousKey = PinKUsed[Pin];
    if(previouseKey == K_1)
      return;
    bool isOwner = zksnarkverify(VK, [
        PIN, 
        K_1
      ],
      proofPINOwnsK);
    if(isOwner && ! KInvalid[K_1]){
      if(previousKey!=0)
        KInvalid[previousKey]=true;
      PinKUsed[Pin]=K_1;
    }
  }

  //PinK=H(Pin, K_1("registerP")) which is != H(Pin, K_1("registerK"))
  //PinK can not be connected to Pin, unless one knows K_1
  function registerP public(
    uint256 PinK,
    uint256 PinKP,
    bytes proof
  ){
    uint256 previousKey = PinKPUsed[PinK]
    if(previousKey == PinK)
      return; //already registered

    //zkp(
      //K!invalid
        //?Need KInvalid to be Zero Knowledge Set (ZKS), and to get roots
      //CA!invalid
      //CA -> K -> Pin
      //PinK=H(Pin, K_1("registerP"))
      //PinKP=H(Pin, K_1("registerP"), P_1("registerP"))
    //)
    bool ok = zksnarkverify(VK, [
    ], proof);

    if(ok && ! PInvalid[PinKP]){
      if(previousKey != 0)
        PInvalid[previousKey]=true;
      PinKPUsed[PinK]=PinKP;
      PinKPLastConfirmed[PinK]=block.number;
    }

  }

}

contract PersonAccount{
}
\end{lstlisting}

\newpage
\section{zkp code}
\begin{lstlisting}[language=C, frame=single, style=b]
//pseudo zokrates zk-SNARK
import "hashes/sha256/512bitPacked" as sha256packed
import "ecc/babyjubjubParams.code" as context
import "ecc/proofOfOwnership.code" as proofOfOwnership

@@

  //end..
}
\end{lstlisting}
\newpage
\section{Problems}
\begin{problem}
  The rate of adding identities, the problem being frequent changes of Merkle Tree Roots, and how long it takes to generate zkp proof, and block generation time.
\end{problem}
\begin{problem}
\label{prob:bigsteal}
  Someone stole $K^{-1}$ before we registered on \pbc.
  The Thief registered $K$ and $P$, and who knows what else.
\end{problem}
\begin{solution}
\end{solution}
\begin{problem}
  Someone stole $K^{-1}$ after we registered on \pbc.
\end{problem}
\begin{problem}
Trying to use unregistered Key.
\end{problem}
\begin{solution}
\end{solution}
\begin{problem}
Trying to register the same PIN with multiple Keys (e.g. two physical ids).
\end{problem}
\begin{problem}
\label{prob:chain}
  Using $P$ without checking the whole $CA\rightarrow K\rightarrow P$ chain.
  \begin{itemize}
    \item Using $P$ to register as a mining key.
    \item Invalidating $P$.
    \item Using $P_{new}$ as a mining key.
  \end{itemize}
\end{problem}
\begin{solution}
  Look at the solution to Problem \ref{prob:miningKey}.

  The Mining Registry can accept new $P$s after an expiration period (which can also be e.g. 1 day).
\end{solution}
\begin{problem}
\label{prob:miningKey}
  A combination of Problem \ref{prob:bigsteal} and Problem \ref{prob:chain}.
  Someone steals $K$, registeres $P$ and registeres $P$ for mining.
  The problem is bigger, because we can't invalidate $P$ if we don't know which $P$ it is.
\end{problem}
\begin{solution}
  We make $P$ renewable. We write the last block number it was renewed on to the blockchain.
  Mining Registry can choose to accept P which is not older than some time period (for the Registry a good period would seem to be 1 day).
  When paying the miners, the Registry also requires proof of $P$'s age.

  $K$ is easely invalidated, because there is an explicit $PIN \rightarrow K^{-1}$ mapping on the blockchain, so it doesn't need to be renewable in the sence to proove it is still valid.
\end{solution}
\begin{problem}
  Only $P$ compromised.
\end{problem}
\end{document}

>>>>

\documentclass{article}
%\documentclass[twocolumn]{article}%
\usepackage[utf8]{inputenc}%
\usepackage{standalone}%
\usepackage{amsmath}%
\usepackage{amsthm}%
\usepackage{amssymb}%
\usepackage{hyperref}%
\usepackage{xcolor}%
\usepackage{tabularx}%
\usepackage{listings}%
\usepackage{colortbl}
\usepackage{enumitem}

\usepackage{listings, xcolor}

\definecolor{verylightgray}{rgb}{.97,.97,.97}

\lstdefinelanguage{Solidity}{
	keywords=[1]{anonymous, assembly, assert, balance, break, call, callcode, case, catch, class, constant, continue, constructor, contract, debugger, default, delegatecall, delete, do, else, emit, event, experimental, export, external, false, finally, for, function, gas, if, implements, import, in, indexed, instanceof, interface, internal, is, length, library, log0, log1, log2, log3, log4, memory, modifier, new, payable, pragma, private, protected, public, pure, push, require, return, returns, revert, selfdestruct, send, solidity, storage, struct, suicide, super, switch, then, this, throw, transfer, true, try, typeof, using, value, view, while, with, addmod, ecrecover, keccak256, mulmod, ripemd160, sha256, sha3}, % generic keywords including crypto operations
	keywordstyle=[1]\color{blue}\bfseries,
	keywords=[2]{address, bool, byte, bytes, bytes1, bytes2, bytes3, bytes4, bytes5, bytes6, bytes7, bytes8, bytes9, bytes10, bytes11, bytes12, bytes13, bytes14, bytes15, bytes16, bytes17, bytes18, bytes19, bytes20, bytes21, bytes22, bytes23, bytes24, bytes25, bytes26, bytes27, bytes28, bytes29, bytes30, bytes31, bytes32, enum, int, int8, int16, int24, int32, int40, int48, int56, int64, int72, int80, int88, int96, int104, int112, int120, int128, int136, int144, int152, int160, int168, int176, int184, int192, int200, int208, int216, int224, int232, int240, int248, int256, mapping, string, uint, uint8, uint16, uint24, uint32, uint40, uint48, uint56, uint64, uint72, uint80, uint88, uint96, uint104, uint112, uint120, uint128, uint136, uint144, uint152, uint160, uint168, uint176, uint184, uint192, uint200, uint208, uint216, uint224, uint232, uint240, uint248, uint256, var, void, ether, finney, szabo, wei, days, hours, minutes, seconds, weeks, years},	% types; money and time units
	keywordstyle=[2]\color{teal}\bfseries,
	keywords=[3]{block, blockhash, coinbase, difficulty, gaslimit, number, timestamp, msg, data, gas, sender, sig, value, now, tx, gasprice, origin},	% environment variables
	keywordstyle=[3]\color{violet}\bfseries,
	identifierstyle=\color{black},
	sensitive=false,
	comment=[l]{//},
	morecomment=[s]{/*}{*/},
	commentstyle=\color{gray}\ttfamily,
	stringstyle=\color{red}\ttfamily,
	morestring=[b]',
	morestring=[b]"
}

\lstset{
	language=Solidity,
	backgroundcolor=\color{verylightgray},
	extendedchars=true,
	basicstyle=\footnotesize\ttfamily,
	showstringspaces=false,
	showspaces=false,
	numbers=left,
	numberstyle=\footnotesize,
	numbersep=9pt,
	tabsize=2,
	breaklines=true,
	showtabs=false,
	captionpos=b
}

@@

\title{Identity Blockchain - Proof of Identity}
\author{
Albert Vučinović, University North\\
Miroslav Jerković, University of Zagreb
}
\begin{document}
\maketitle

\begin{abstract}
$\pbc$ uses state-certified electronic identities (eIDs) to create blockchain identities and a consensus protocol called Proof of Identity (PoI). PoI is "green" and enables many applications that are impossible to implement without verified identity on the blockchain, e.g., direct democracy and universal basic income, encrypted messaging, etc. $\pbc$ preserves identity anonymity by using zk-SNARKs and an anonymization protocol for identity onboarding.
\end{abstract}

\section{Introduction}
TODO

\section{Notation}
\vspace{10px}
 \arrayrulecolor{gray}
\begin{tabular}{p{0.16\linewidth}| p{0.84\linewidth}}
  $(K, K^{-1})$ & \ \ Pair of public key $K$ and the corresponding private key $K^{-1}$ \\[3px]
	$K(value)$ & \ \ String $value$ encrypted with a public key $K$ \\[3px]
	$K^{-1}(value)$ & \ \ String $value$ encrypted with a private key $K^{-1}$ \\[3px]
  $H$ & \ \ zk-SNARK-friendly hash function \\[5px]
 \hline \\
   $Nin$ & \ \ Unique state-issued personal \textit{National Identification Number}\\[3px]
   $CA$ & \ \ Certificate Authority \\[3px]
   $eID$ & \ \ Electronic identification document \\[3px]
	$\kid$ & \ \ CA-certified public key of eID\\[3px]
  $\khk$ & \ \ Person key, unique public key used to access \pbc{}

\end{tabular}

\vspace{15px}

@@

\newpage
\section{Registering $\kid$}
Register $\kid$ on \pbc{} by calling $$register\kid(H(Nin), \kid^{-1}("register\kid"), proofNinOwnsKid).$$
\begin{enumerate}[leftmargin=0cm]
\item[] \underline{Pseudo-solidity code}

\hfill\begin{minipage}{\dimexpr\textwidth-20px}
\begin{lstlisting}[language=Solidity]
  mapping(uint256 => uint256) public ninKidUsed;
  mapping(uint256 => bool) public kidInvalid;

  function registerKid(
    uint256 hNin, // hNin = H(Nin)
    uint256 vKid, // vKid = KidPrivate("registerKid")
    bytes proofNinOwnsKid
  ) public {
    uint256 previousKey = ninKidUsed[hNin];
    if (previousKey == vKid) return; // already registered
    bool isOwner = zksnarkverify(VK, [hNin, vKid], proofNinOwnsKid); // VK = verification key
    if (isOwner && !kidInvalid[vKid]) {
      if (previousKey != 0) kidInvalid[previousKey] = true;
      ninKidUsed[hNin] = vKid;
    }
  }
\end{lstlisting}
\xdef\tpd{\the\prevdepth}
\end{minipage}
\item[] \underline{Features}
    \begin{itemize}
      \item[] \textbf{Sybil resistance} \\ A Person is prevented from registering more than one $\khk$, e.g. by using different identification documents issued for the same $Nin$.
          \vspace{5px}
      \item[] \textbf{Fix for the loss of eID} \\ A Person who has lost a previously registered $\kid$, e.g. due to loss of eID, can overwrite it by registering a new $\kid$.
          \vspace{5px}
      \item[] \textbf{Identity theft damage control} \\ If a Person overwrites the previous $\kid$ with a new one, the identity Thief loses access to services that verify the entire identity chain.
    \end{itemize}

\item[] \underline{Remarks}
\begin{itemize}
\item[i)] An entity that knows $\kid$, e.g. the CA who certified the corresponding eID, can know that the Person has registered $\kid$ on \pbc{}.
\item[ii)] Reasoning behind the choice of arguments: if $H(Nin, \kid^{-1}("register\kid"))$ was used as an argument, then TODO. On the other hand, the choice of arguments $Nin$ and $\kid^{-1}("register\kid")$ would TODO.
\end{itemize}
\end{enumerate}

\newpage
\section{Registering $\khk$}
Register $\khk$ on \pbc{} by calling $$register\khk(Nin\kid, Nin\kid\khk, proof),$$
  where:
    \begin{enumerate}
      \item[] $Nin\kid=H(Nin,\kid^{-1}("register\khk"))$
      \item[] $Nin\kid\khk=H(Nin, \kid^{-1}("register\khk"), \khk^{-1}("register\khk"))$.
    \end{enumerate}
\begin{enumerate}[leftmargin=0cm]
\item[] \underline{Pseudo-solidity code}

\hfill\begin{minipage}{\dimexpr\textwidth-20px}
\begin{lstlisting}[language=Solidity]
  mapping(uint256 => uint256) public ninKidKpUsed;
  mapping(uint256 => bool) public kpInvalid;
  mapping(uint256 => uint256) public ninKidKpLastConfirmed;

  function registerKp(
    uint256 ninKid,
    uint256 ninKidKp,
    bytes proof
  ) public {
    uint256 previousKey = ninKidKpUsed[ninKid];
    if (previousKey == ninKid) return; // already registered
    bool ok = zksnarkverify(VK, [ninKid, ninKidKp], proof); // VK = verification key
    if (ok && !kpInvalid[ninKidKp]) {
      if (previousKey != 0) kpInvalid[previousKey] = true;
      ninKidKpUsed[ninKid] = ninKidKp;
      ninKidKpLastConfirmed[ninKid] = block.number;
    }
  }
\end{lstlisting}
\xdef\tpd{\the\prevdepth}
\end{minipage}
\item[] \underline{Features}
\begin{itemize}
      \item[] \textbf{Sybil resistance} \\ $\khk$ is a unique public key bound to the Person on the \pbc{}. By design, the Person cannot have two valid $\khk$ keys at the same time.

      TODO: Explanation/proof.
      \vspace{5px}
    \item[] \textbf{Anonimity} \\ No one who has a database with all public keys $\kid$ or/and public keys $\khk$ can tell, from the function call, which $Nin$, $\kid$ or $\khk$ was used. This is true under the assumption that CA, which certified the eID, does not have access to $\kid^{-1}$, i.e. that $\kid$ was securely generated on the eID.

    TODO: Explanation/proof.
\end{itemize}

\item[] \underline{Remarks}
\begin{itemize}
\item[i)] Reasoning behind the choice of arguments: TODO
\end{itemize}

\end{enumerate}

\newpage
\section{zkp code}
\begin{lstlisting}
//pseudo zokrates zk-SNARK
import "hashes/sha256/512bitPacked" as sha256packed
import "ecc/babyjubjubParams.code" as context
import "ecc/proofOfOwnership.code" as proofOfOwnership

@@

  //end..
}
\end{lstlisting}
\newpage
\section{Problems}
\begin{enumerate}[label=\textbf{P\arabic*}]
\item The rate of addition of identities, the problems of frequent changes of Merkle Tree Roots, and how long it takes to generate zkp proof, and block generation time.
\item \label{bigsteal} The Thief stole $\kid^{-1}$ before we registered on \pbc{} and then registered $\kid$ and $\khk$.
\item The Thief stole $\kid^{-1}$ after we registered on \pbc.
\item Trying to use unregistered Key.
\item Trying to register the same $Nin$ with multiple Keys (e.g. two physical ids).
\item \label{chain} Using $\khk$ without checking the whole $CA\rightarrow \kid \rightarrow \khk$ chain.
  \begin{itemize}
    \item[i)] Using $\khk$ to register as a mining key.
    \item[ii)] Invalidating $\khk$.
    \item[iii)] Using new $\khk$ as a mining key.
  \end{itemize}
  \underline{Solution}

  Look at the solution to \ref{miningKey}.

  The Mining Registry can accept new $\khk$ after an expiration period (which can be e.g. one day).
\item \label{miningKey} A combination of \ref{bigsteal} and \ref{chain}. The Thief steals $\kid$, registers $\khk$ and registers $\khk$ for mining. The problem is bigger, because we can't invalidate $\khk$ if we don't know which $\khk$ it is.

  \underline{Solution}

  We make $\khk$ renewable. We write the last block number it was renewed on to the \pbc.
  Mining Registry can choose to accept $\khk$ that is not older than some time period (for the Registry a good period would seem to be one day).
  When paying the miners, the Registry also requires proof of $\khk$.
\item Only $\khk$ is compromised.
\end{enumerate}
\end{document}
